\documentclass[11pt]{article} %Sets the default text size to 11pt and class to article.
%------------------------Dimensions--------------------------------------------
\topmargin=0.0in %length of margin at the top of the page (1 inch added by default)
\oddsidemargin=0.0in %length of margin on sides for odd pages
\evensidemargin=0in %length of margin on sides for even pages
\textwidth=6.5in %How wide you want your text to be
\marginparwidth=0.5in
\headheight=0pt %1in margins at top and bottom (1 inch is added to this value by default)
\headsep=0pt %Increase to increase white space in between headers and the top of the page
\textheight=9.0in %How tall the text body is allowed to be on each page
\begin{document}
\centerline{{\LARGE \bf Xiaohui Qi}}
\centerline{208 lyon street. $\bullet$ cincinnati,45219 $\bullet$ (513)652-2075}
\centerline{qixiaohuihaha@gmail.com}
\noindent
\line(1,0){470}
\\
\\  %This is the same as a return in Latex
\noindent {\Large \bf Professional Summary} %dont indent this line and make it bold and large
\\
\\
\noindent 
A diligent researcher and also a team player, with a broaden knowledge in many languages from computer software to FPGA and embedded system, dedicate in using the skills to create something useful and applicable. Willing to take new challenges and appreciate the importance of team-work.
\bigskip %This makes a large line skip (\smallskip is also a command but has a smaller gap
\\
\noindent{\Large \bf Core Competences}
\\

\noindent %Make sure that there is no line skip for as long as you want this effect
Can Program in a large variety of languages including: \\ %The \\ is the same as a return
\centerline{\hfill $\bullet$ C++ \hfill $\bullet$ Python \hfill $\bullet$ Perl\hfill}\\
\centerline{\hfill $\bullet$ Java \hfill $\bullet$ Ruby \hfill $\bullet$ VHDL\hfill}\\
\centerline{\hfill $\bullet$ Verilog \hfill $\bullet$ Hspice \hfill $\bullet$ Irsim\hfill}\\
Proficeint with the following engineering applications: \\
\centerline{\hfill $\bullet$ MatLab \hfill $\bullet$ eclipse \hfill $\bullet$ quartus II\hfill}\\
\centerline{\hfill $\bullet$ modelsim \hfill $\bullet$ Visula C++ \hfill $\bullet$ Latex \hfill}\\
\\
Other languages and tools: html, css, magic, microsoft office, Linux and Windows OS, mySQL, cscope.
\\
\\
\noindent{\Large \bf Education}
\\
\noindent
\\
 University of Cincinnati, Ohio \hfill june 2014 \\
                Meng, Electrical Engineering\\
                Track: VLSI \\
                GPA: 3.7/4.0 \\
                Courses plan to take spring semester: Network Security, Introduction to Communication Systems, VLSI Design for Test and Power, VLSI Design Automation
\\ 
\noindent
\\
			    University of Shandong, Shandong\hfill june 2013  \\
                B.S, Electrical Engineering  \\ 
                GPA: 3.0/4.0 
\\
\noindent
\\ Bilingual proficient in English and Chinese
\\
\\
\noindent{\Large \bf Research Experiences}
\\
\noindent
\\
$\bullet$ Working with Altera DE1 FPGA embedded system board, and using the Nios II micro-system wrote a program that can use the connected microphone record the sound information(sample the sound in very high speed and record the amplitude and frequency of the sample sound), then replay the sound in different mode: add echo effect, filter the background noise, display the waveform of the sound on a VGA device. Also in addition if the embedded system is connected to a keyboard using PS 2 port then it also simulate the piano sounds by pressing different keys on keyboard.
\\
$\bullet$ Using magic designed a 16x16 series in parallel out micro chip, when the 16 bit data is hold in a 16 bit register the 16 bit parallel output port can read from the input, and each bit can read any of the 16 input bits. The chip use 256 D flip flop register to store all the data and another extra 16 registers to hold the input and output vales, also the chip has debug mode so that each bit of the output data can be directly read from outside port. Also in testing I exhaustive test the chip, I wrote a python script that can generate all the 65536 test cases in Irsim cmd file. 
\\
$\bullet$ Wrote a android application that can transmit word document on the phone via bluetooth to other phone.If the word document is in SD card, then the application can read the content of the sd card then display the documents end with .doc or .docx. Also the application can transmit data to a pc as long as the phone and the pc are in the same network. 
\\
$\bullet$ Wrote a microprocessor using verilog on a DE 1 FPGA board. The microprocessor has 16 bit registers and contains a full adder/subtracter, and a fsm control unit, a multiplexer, a counter, a memory block, so that the instructions can be read from the memory and a 7 segment lcd display. The microprocessor has 7 instructions: mov, movi, add, sub, ld(load), st(store), movnz(move if not zero), also the lcd display can display information regarding the instruction, result of add/sub etc.
\\
$\bullet$ Take part in freescale intelligent car competition, the intelligent car can run on a specific kind of racing track which has black duct tape in the middle, by analysing the data procured from the camera on top of the car and taking the velocity of the car into consideration the car will make decision on how it will turn and whether to accelerate or decelerate so it can keep on track and finish the race as fast as it can.
\\
\\
\noindent{\Large \bf Awards}
\\
\\
Wining the first prize in the university for participating in the Unicom Cup
Seven Day Business Creation Plan by writing a android app that can control a toy car driving, turning,accelerating and decelerating through bluetooth \hfill Spring 2012
\\
\\
Wining of the second prize in Shandong Competition Zone in Freescale Cup competition for College Students on Intelligent Vehicle Design.\hfill Spring 2011
\\
\\
Wining the third prize in the university for designing a multifunctional water heating device using single chip machine. \hfill Fall 2010
\\
\\
\noindent{\Large \bf Social Activity}
\\
\\
Took part in the survey about people's attitude of the air condition and opinion on how does pollution affect their everyday live. \hfill Fall 2011
\\
\\
Attend a campus activity group that helps senior citizens do chores and laundries etc.\hfill Spring 2010
\\
\\
Being volunteer in Samsung marathon race. \hfill Fall 2009

\end{document}